SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-04-27 SI.tex
Update
Update text.

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage{xr}

@@

\author[1]{Anne M. Kiirikki}         %ORCID: ?
\author[2]{Hanne S. Antila}          %ORCID: 0000-0002-2474-5053
\author[3]{Lara S. Bort}             %ORCID: ?
\author[4]{Pavel Buslaev}         %ORCID: 0000-0003-2031-4691
\author[5]{Fernando Favela-Rosales}
\author[6]{Tiago Mendes Ferreira}
\author[7,8]{Patrick F.J. Fuchs}
\author[9]{Rebeca Garcia-Fandino}
\author[10]{Ivan Gushchin}
%\author[2]{Matti Javanainen}      %ORCID: 0000-0003-4858-364X
\author[11,12]{Batuhan Kav}           %ORCID: 0000-0003-4990-373X
\author[22]{Norbert Ku{\v c}erka}
\author[13]{Patrik Kula}
\author[14]{Milla Kurki}
\author[10]{Alexander Kuzmin}
\author[15,16]{Jesper J. Madsen}  %ORCID: 0000-0003-1411-9080
\author[17,18]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
%\author[2]{...}                   %ORCID: ?
\author[1]{Ricky Nencini}
\author[19]{Thomas Piggot}
\author[20]{{\'A}ngel Pi{\~n}eiro}
\author[10]{Suman Samantray}
\author[9,20,21]{Fabi{\'a}n Suarez-Leston}
\author[1,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Department of Theory \& Bio-Systems and Department of Biomaterials, Max Planck Institute of Colloids and Interfaces, Germany}
\affil[3]{University of Potsdam, Institute of Physics and Astronomy, Potsdam-Golm, 14476, Germany}
%\affil[2]{Affiliation, department, city, postcode, country}
\affil[4]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, Jyv{\"a}skyl{\"a}, 40014 , Finland}
\affil[5]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[6]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[7]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[8]{Universit{\'e} Paris Cit{\'e}, UFR Sciences du Vivant, Paris, 75013, France}
\affil[9]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[10]{no affiliation}
\affil[11]{Institute of Biological Information Processing: Structural Biochemistry (IBI-7), Forschungszentrum Jülich, Jülich 52428, Germany}
\affil[12]{ariadne.ai GmbH (Germany), Häusserstra{\ss}e 3 Heidelberg 69115, Germany }
\affil[13]{Institute of Organic Chemistry and Biochemistry of the Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2,  Prague, CZ-16610, Czech Republic}
\affil[14]{School of Pharmacy, University of Eastern Finland, 70211 Kuopio, Finland}
\affil[15]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[16]{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[17]{Department of Chemistry, University of Bergen, Norway}
\affil[18]{Computational Biology Unit, Department of Informatics, University of Bergen, Norway}
\affil[19]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}
\affil[20]{Department of Applied Physics, Faculty of Physics, University of Santiago de Compostela, Santiago de Compostela, E-15782, Spain}
\affil[21]{MD.USE Innovations S.L., Edificio Emprendia, 15782 Santiago de Compostela, Spain}
\affil[22]{Department of Physical Chemistry of Drugs and Faculty of Pharmacy, Comenius University Bratislava, 832 32 Bratislava, Slovakia}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[height = 0.85\textheight]{Figures/totalrankingCOMPL.pdf}
    \caption{Top 50 simulations in the NMRlipids Databank ranked based on the C--H bond order parameter quality against experiments. The columns 2-4 show qualities for acyl chain order parameters ($P^\mathrm{tails}$), headgroup order parameters ($P^\mathrm{hg}$), all order parameters ($P^\mathrm{total}$), and for X-ray scattering form factors ($FF_q$). Column 5 shows relative equilibration times for conformations ($\tau_\mathrm{rel}$). Note that the best possible order parameter quality is one, while the best possible form factor quality is zero. ID values in the last column can be used to identify each simulation in the databank.}
    \label{fig:top50simulations}
\end{figure}

>>>>

\documentclass[fleqn,10pt]{wlscirepSI}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage{xr}

@@

\author[1]{Anne M. Kiirikki}         %ORCID: ?
\author[2,3]{Hanne S. Antila}          %ORCID: 0000-0002-2474-5053
\author[2,4]{Lara S. Bort}             %ORCID: ?
\author[5]{Pavel Buslaev}         %ORCID: 0000-0003-2031-4691
\author[6]{Fernando Favela-Rosales}
\author[7]{Tiago Mendes Ferreira}
\author[8,9]{Patrick F.J. Fuchs}
\author[10]{Rebeca Garcia-Fandino}
\author[11]{Ivan Gushchin}
%\author[2]{Matti Javanainen}      %ORCID: 0000-0003-4858-364X
\author[12,13]{Batuhan Kav}           %ORCID: 0000-0003-4990-373X
\author[14]{Norbert Ku{\v c}erka}
\author[15]{Patrik Kula}
\author[16]{Milla Kurki}
\author[11]{Alexander Kuzmin}
\author[17,18]{Jesper J. Madsen}  %ORCID: 0000-0003-1411-9080
\author[2,19,20]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
%\author[2]{...}                   %ORCID: ?
\author[1]{Ricky Nencini}
\author[21]{Thomas J. Piggot}
\author[22]{{\'A}ngel Pi{\~n}eiro}
%\author[11]{Suman Samantray} %ORCID: 0000-0003-3361-9582
\author[10,22,23]{Fabi{\'a}n Su{\'a}rez-Lest{\'o}n}
\author[1,24,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[3]{Department of Biomaterials, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[4]{University of Potsdam, Institute of Physics and Astronomy, Potsdam-Golm, 14476, Germany}
%\affil[2]{Affiliation, department, city, postcode, country}
\affil[5]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, Jyv{\"a}skyl{\"a}, 40014 , Finland}
\affil[6]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[7]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[8]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[9]{Universit{\'e} Paris Cit{\'e}, UFR Sciences du Vivant, Paris, 75013, France}
\affil[10]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[11]{no affiliation}
%Physical and Computational Sciences Division, Pacific Northwest National Laboratory, Richland, Washington 99352, United States
\affil[12]{Institute of Biological Information Processing: Structural Biochemistry (IBI-7), Forschungszentrum Jülich, Jülich 52428, Germany}
\affil[13]{ariadne.ai GmbH (Germany), Häusserstra{\ss}e 3 Heidelberg 69115, Germany }
\affil[14]{Department of Physical Chemistry of Drugs and Faculty of Pharmacy, Comenius University Bratislava, 832 32 Bratislava, Slovakia}
\affil[15]{Institute of Organic Chemistry and Biochemistry of the Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2,  Prague, CZ-16610, Czech Republic}
\affil[16]{School of Pharmacy, University of Eastern Finland, 70211 Kuopio, Finland}
\affil[17]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[18]{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[19]{Department of Chemistry, University of Bergen, 5020 Bergen, Norway}
\affil[20]{Computational Biology Unit, Department of Informatics, University of Bergen, 5020 Bergen, Norway}
\affil[21]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}
\affil[22]{Department of Applied Physics, Faculty of Physics, University of Santiago de Compostela, Santiago de Compostela, E-15782, Spain}
\affil[23]{MD.USE Innovations S.L., Edificio Emprendia, 15782 Santiago de Compostela, Spain}
\affil[24]{VTT Technical Research Centre of Finland, Espoo, Finland}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[height = 0.8\textheight]{Figures/totalrankingCOMPL.pdf}
    \caption{Top 50 simulations in the NMRlipids Databank ranked based on the C--H bond order parameter quality against experiments. The columns 2-4 show qualities for acyl chain order parameters ($P^\mathrm{tails}$), headgroup order parameters ($P^\mathrm{hg}$), all order parameters ($P^\mathrm{total}$), and for X-ray scattering form factors ($FF_q$). Column 5 shows relative equilibration times for conformations ($\tau_\mathrm{rel}$). Note that the best possible order parameter quality is one, while the best possible form factor quality is zero. ID values in the last column can be used to identify each simulation in the databank.}
    \label{fig:top50simulations}
\end{figure}
